This PDF is a Git Repository\\Containing its Own \LaTeX\ Source

### 2017-05-01 article.tex
It turns out we can have 0xFFFF byte objects, after all!
More text in the article.

\begin{center}
%%\includegraphics[width=0.5\hsize]{RazvodityeKrolikov_small}
\end{center}

Okay, the next step is to figure out the ``chunk'' format.  The chunk
header is variable length, and can be as small as one byte. It encodes
the type of object and the \emph{uncompressed} size of the object. If
the object is a \textit{delta} (\textit{i.e.}, a diff, as opposed to a
complete object), the header is followed by either the SHA-1 hash of
the base object to which the delta should be applied, or a byte
reference within the packfile for the start of the base object. The
remainder of the chunk consists of the object data, zlib-compressed.
\begin{center}
{\newcount\bitnum\bitnum=0
\begin{tikzpicture}
\node[coordinate] at (0,0) (b0) {};
\foreach \i in {1,0,1,1,0,1,0,0,0,1,0,1,0,1,1,0} {
  {\newcount\prevbit\prevbit=\bitnum
  \global\advance\bitnum by 1
  \node[anchor=west] at (b\the\prevbit.east) (b\the\bitnum) {\i};}
  \draw ([xshift=1pt]b\the\bitnum.south west) -- ([xshift=-1pt]b\the\bitnum.south east);
}
\end{tikzpicture}}
\end{center}

>>>>

\begin{center}
\includegraphics[width=0.5\hsize]{RazvodityeKrolikov_small}
\end{center}

Okay, the next step is to figure out the ``chunk'' format.  The chunk
header is variable length, and can be as small as one byte. It encodes
the type of object and the \emph{uncompressed} size of the object. If
the object is a \textit{delta} (\textit{i.e.}, a diff, as opposed to a
complete object), the header is followed by either the SHA-1 hash of
the base object to which the delta should be applied, or a byte
reference within the packfile for the start of the base object. The
remainder of the chunk consists of the object data, zlib-compressed.

This is the format of the variable length chunk header:
\begin{center}
{\newcount\bitnum\bitnum=0
\begin{tikzpicture}
\node[coordinate] at (0,0) (b0) {};
\foreach \i in {1,0,1,1,0,1,0,0,1,1,0,1,0,1,1,0,0,1,0,0,1,0,0,1} {
  {\newcount\prevbit\prevbit=\bitnum
  \global\advance\bitnum by 1
  \node[anchor=west] at (b\the\prevbit.east) (b\the\bitnum) {\i};}
  \draw ([xshift=1pt]b\the\bitnum.south west) -- ([xshift=-1pt]b\the\bitnum.south east);
}
\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=-2pt
    },
    decorate
] ([xshift=-1pt]b8.north east) -- ([xshift=1pt]b1.north west)
node [pos=0.5,anchor=south,yshift=-2pt] {\footnotesize first byte};
\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=-2pt
    },
    decorate
] ([xshift=-1pt]b16.north east) -- ([xshift=1pt]b9.north west)
node [pos=0.5,anchor=south,yshift=-2pt] {\footnotesize second byte};
\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=-2pt
    },
    decorate
] ([xshift=-1pt]b24.north east) -- ([xshift=1pt]b17.north west)
node [pos=0.5,anchor=south,yshift=-2pt] {\footnotesize third byte};

\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=2pt
    },
    decorate
] ([xshift=1pt]b2.south west) -- ([xshift=-1pt]b4.south east)
node [pos=0.5,yshift=-2pt,anchor=north] (type) {\footnotesize object type};

\draw[<-] (b1) -- (type.south -| b1) node[anchor=north,align=center,font=\footnotesize] {if the MSB is one,\\then this is not\\the last byte};

\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=2pt
    },
    decorate
] ([xshift=1pt]b5.south west) -- ([xshift=-1pt]b8.south east)
node [pos=0.5,yshift=-2pt,anchor=north,align=center,font=\footnotesize] (length) {first four\\bits of\\the length\\(big-endian)};

\draw[<-] (b9) -- (length.south -| b9) node[anchor=north,align=center,font=\footnotesize] {MSB is one,\\so this is \emph{not} the last byte};

\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=2pt
    },
    decorate
] ([xshift=1pt]b10.south west) -- ([xshift=-1pt]b16.south east)
node [pos=0.5,yshift=-2pt,anchor=north,align=center,font=\footnotesize] (next) {the next seven\\bits of the length\\(big-endian)};

\draw[<-] (b17) -- (next.south -| b17) node[anchor=north,align=center,font=\footnotesize] {MSB is zero,\\so this is the last byte};

\draw [
    thick,
    decoration={
        brace,
        mirror,
        raise=2pt
    },
    decorate
] ([xshift=1pt]b18.south west) -- ([xshift=-1pt]b24.south east)
node [pos=0.5,yshift=-2pt,anchor=north,align=center,font=\footnotesize] {the next seven\\bits of the length\\(big-endian)};

\end{tikzpicture}}
\end{center}
This example header represents an object of type \texttt{0b011}, which
happens to be a git blob, and an \emph{uncompressed} length of
$(100_2\,\verb|<<|\,14) +
(1010110_2\,\verb|<<|\,7) + 1001001_2
= 76617$ bytes.  Since this is not a delta object, it is immediately
followed by the zlib-compressed object data.

%% TODO: Talk about the Delta Ref file format

\section{A Minimal Polyglot PoC}

We now know that a git bundle is really just a git packfile with an
additional header, and a git packfile stores individual objects using
zlib, which uses the DEFLATE compression algorithm. DEFLATE supports
zero compression, so if we can store the PDF in a single object (as
opposed to it being split into deltas), then we could theoretically
coerce it to be intact within a valid git bundle.

Forcing the PDF into a single object is easy: We just need to add it
to the repo last, immediately before generating the bundle.

Getting the object to be compressed with zero compression is also
relatively easy.  That's because git was built in almost religious
adherence to The UNIX Philosophy: It is architected with hundreds of
sub commands it calls ``plumbing,'' of which the vast majority you
will likely have never heard. For example, you might be aware
that \texttt{git pull} is equivalent to a \texttt{git fetch} followed
by a \texttt{git merge}. In fact, the \texttt{pull} code is actually
spawning a new \texttt{git} child process to execute each of those
subcommands. Likewise, the \texttt{git bundle} command spawns
a \texttt{git pack-objects} to generate the packfile portion of the
bundle.  All we need to do is inject the \texttt{--compression=0}
argument into the list of command line arguments passed
to \texttt{pack-objects}.  This is a one-line addition
to \texttt{bundle.c}:\\
{\footnotesize
{\color{gray}
\verb|    argv_array_pushl(&pack_objects.args,|\\
\verb|                     "pack-objects", "--all-progress-implied",|}\\
\verb|                     "--compression=0",|\\
{\color{gray}
\verb|                     "--stdout", "--thin", "--delta-base-offset",|\\
\verb|                     NULL);|
}}

Using our patched version of git, every object stored in the bundle
will be uncompressed!
\begin{center}
\begingroup
\setbox9=\hbox{\footnotesize\verb|$ git bundle create article_bundle.pdf --all|}
\begin{minipage}{\wd9}
\footnotesize\begin{verbatim}
$ export PATH=/path/to/patched/git:$PATH
$ git init .
$ git add article.pdf
$ git commit article.pdf -m "added"
$ git bundle create polyglot.pdf --all
\end{verbatim}
\end{minipage}
\endgroup
\end{center}
